---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# prego

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/prego)](https://CRAN.R-project.org/package=prego)
<!-- badges: end -->

The `prego` package implements simple regression algorithms for finding motifs in DNA. You can either use it to find motif which are discriminating between two or more clusters of DNA sequences, or for generating motifs from one or more continuous variables.

The PREGO algorithm is described [here](https://doi.org/10.1101%2Fgr.5113606).

## Installation

You can install the development version of prego like so:

``` r
remotes::install_github("tanaylab/prego")
```

## Usage

```{r}
library(prego)
```

For a set of continuous variables:

```{r}
res <- regress_pwm(sequences_example, response_mat_example)
plot_regression_qc(res)
```

For binary response: 

```{r}
res_binary <- regress_pwm(cluster_sequences_example, cluster_mat_example[, 1])
plot_regression_qc(res_binary)
```

For clusters of sequences:

```{r}
res <- regress_pwm.clusters(cluster_sequences_example, clusters_example)
res$stats
```

